---
title: "Two Parameters"
author: "Nihal Neeraj"
format: html
execute: 
  echo: false
---


```{r}
#| message: FALSE

library(tidyverse)
library(primer.data)
library(brms)
library(tidybayes)
library(gtsummary)
```


```{r}
nhanes |>
  filter(sex == "Male", age >= 18) |>
  select(height) |>
  drop_na() |>
  ggplot(aes(x = height)) +
  geom_histogram(bins = 50) +
  labs(title = "Male Adult Height in the US in 2010",
       caption = "Source: National Health and Nutrition Examination",
       x = "Height(cm)",
       y = "Count")
```

```{r}
#| cache: true

fit_male_height <- brm(formula = height ~ 1,
    data = nhanes,
    family = gaussian(),
    silent = 2,
    refresh = 0,
    seed = 12)
```

```{r}
tbl_regression(fit_male_height, intercept = TRUE)
```

The nhanes data set from the National Health and Nutrition Examination Survey conducted from 2009 to 2011 by the Centers for Disease Control and Prevention, is used to make a table with which we can then answer the question on what is the average height. However, one specific problem that causes doubt is on if the dataset used is inaccurate, which means that it would question the reliability of the calculated average height. We used a model to determine the average height of a man in the U.S this model was made from a table which gave all the information on the height of men in the U.S. The dependent variable in this case would be the height.

```{r}
ndata <- tibble(.rows = 1)
```

```{r}
fit_male_height |>
  add_predicted_draws(newdata = ndata) |>
  ggplot(aes(x = .prediction)) +
  geom_histogram(aes(y = after_stat(count/sum(count))), bins = 100) +
  labs(
    title = "Posterior for height of Random Male",
    subtitle = "Uncertanty for a single individual is much greater than for the expected value",
    x = "Height (cm)",
    y = "Probability",
    caption = "Source: NHANES"
  ) +
  scale_x_continuous(labels = scales::number_format()) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))
```

```{r}
fit_male_height |>
  add_predicted_draws(newdata = ndata) |>
  mutate(tall = if_else(.prediction > 180, TRUE, FALSE)) |>
  summarize(odds = mean(tall))
```

The nhanes data set from the National Health and Nutrition Examination Survey conducted from 2009 to 2011 by the Centers for Disease Control and Prevention, is used to make a table with which we can then answer the question on what is the average height. However, one specific problem that causes doubt is on if the dataset used is inaccurate, which means that it would question the reliability of the calculated average height. We used a model to determine the average height of a man in the U.S this model was made from a table which gave all the information on the height of men in the U.S. The dependent variable in this case would be the height. The quantity of interest (QoI) is the average height of a man in the U.S., and the model estimates this average with a 95% confidence interval, providing a measure of uncertainty and ensuring the robustness of the estimate despite potential data inaccuracies.
